---
title: "Ryoak Analysis"
author: "John H. Freeman"
date: "5/7/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(gdata)
require(MASS)
require(broom)
```

#Exploration of Categorical Variables

```{r echo=FALSE}
industrialsales <- read.xls("spreadsheet.xlsx")
industrialsales.trim <- industrialsales[complete.cases(industrialsales[,"Price.Per.SF"]),]
industrialsales.trim <- industrialsales.trim[complete.cases(industrialsales.trim[,"Percent.Office"]),]
industrialsales.trim <- industrialsales.trim[complete.cases(industrialsales.trim[,"Condition"]),]
ggplot(industrialsales.trim, aes(Percent.Office,Price.Per.SF)) +
  geom_point() + 
  stat_smooth(method = "lm") + 
  facet_wrap(~Condition)
```
It appears that there is no difference graphically in price per squarefoot for average rated properties as percentage of office increases.

However, for "Good" rated properties there appears to be an effect on price per squarefoot as the percentage of office increases.

There are only solitary points for "fair" and "avg to good" properties.

##Transforming price per squarefoot

```{r echo=FALSE}
industrialsales.good <- industrialsales.trim[industrialsales.trim$Condition=="Good",]
lm1 <- lm(Price.Per.SF ~ Percent.Office, data = industrialsales.good)
bc <- boxcox(Price.Per.SF ~ Percent.Office, data=industrialsales.good, lambda = seq(-2,2,.01), plotit = FALSE)
bc$x[which.max(bc$y)]
industrialsales.good$Price.Per.SF0.05 = industrialsales.good$Price.Per.SF^bc$x[which.max(bc$y)]

ggplot(industrialsales.good, aes(Percent.Office, Price.Per.SF0.05)) +
  geom_point() + 
  stat_smooth(method = "lm")
```

Transforming Price per Square foot by `r bc$x[which.max(bc$y)]` reveals a better predictive relationship however.

```{r echo=FALSE}
industrialsales.good$Office.SF <- industrialsales.good$Net.Rentable.Area * industrialsales.good$Percent.Office
industrialsales.good$Warehouse.SF <- industrialsales.good$Net.Rentable.Area * (1-industrialsales.good$Percent.Office)
lm2 <- lm(Price.Per.SF0.05 ~ Percent.Office, data=industrialsales.good)
summary(lm2)
tidy2 <- tidy(lm2)
tidy2
```

From this relationship that for properties classified as good, that with no office space the base price per squarefoot is \$`r tidy2[1,2]` per Square Foot and increases by \$`r tidy2[2,2]` per Square Foot by each percentage increase in office space.